
% Acknowledgement
\chapter*{Acknowledgement}
\addcontentsline{toc}{chapter}{Acknowledgement}

First and foremost, I express my deepest gratitude to the Almighty for granting me the strength, patience, and perseverance to complete this project successfully.

I would like to extend my sincere appreciation to my supervisor, A. F. M. Mahbubur Rahman, Associate Professor, Department of Computer Science and Engineering, University of Rajshahi, for their invaluable guidance, continuous support, and constructive feedback throughout the development of this project. Their expertise and insights have been instrumental in shaping this work.

I am deeply grateful to Md. Rokanujjaman, Head of the Department of Computer Science and Engineering, for providing the necessary facilities and creating an encouraging academic environment that enabled me to pursue this research.

I would also like to thank all the faculty members of the Department of Computer Science and Engineering for their teaching, mentorship, and support during my academic journey. Their knowledge and dedication have been a constant source of inspiration.

My heartfelt thanks go to my family members for their unconditional love, encouragement, and unwavering belief in my abilities. Their sacrifices and support have been the foundation of my academic achievements.

I am thankful to my friends and fellow students who provided valuable suggestions, assistance, and moral support during the challenging phases of this project. Their collaboration and camaraderie made this journey more meaningful and enjoyable.

Finally, I acknowledge all the researchers, developers, and open-source communities whose work and contributions in the fields of system monitoring, dynamic instrumentation, and web technologies have provided the theoretical foundation and practical tools for this project.

\vspace{1cm}
\begin{flushright}
Md. Jahangir Alam\\
Student ID: 2011076129\\
Session: 2019-20\\
Department of Computer Science and Engineering\\
University of Rajshahi
\end{flushright}